Figures

### 2018-10-11 figures/02_hierarchical_demo.Rmd
finish out hierarchical demo figure

```{r hu4_n, echo=FALSE, message=TRUE, eval=FALSE}
library(kableExtra)
library(dplyr)
library(magrittr)

library(LAGOSextra)
library(sf)
library(ggplot2)

# setwd("tables")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

ggplot() +
  geom_sf(data = hu4, aes(fill = n)) +
  theme_minimal()

@@

```{r }

```

>>>>

```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
library(kableExtra)
library(dplyr)
library(tidyr)
library(magrittr)

library(LAGOSNE)
library(LAGOSextra)
library(sf)
library(ggplot2)
library(cowplot)

# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

@@

```{r 02_hierarchical_demo, fig.height=3}
lg <- lagosne_load("1.087.1")

dt <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
                summarize(
                  group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
                           lagoslakeid), 
                  tp = median(tp, na.rm = TRUE), 
                  chla = median(chla, na.rm = TRUE))
                ) %>%
  tidyr::drop_na()

# hist(as.vector(table(dt$hu4_zoneid)))  
good_hu4s <- group_by(dt, hu4_zoneid) %>% 
  tally() %>%
  dplyr::filter(n > 220)  
dt <- dplyr::filter(dt, hu4_zoneid %in% good_hu4s$hu4_zoneid)
dt <- dplyr::filter(dt, tp < 500 & chla < 150)

plot_grid(
  ggplot(data = dt, aes(x = tp, y = chla, color = hu4_zoneid)) + 
    geom_point(alpha = 0.5) +
    geom_smooth(method = lm, se = FALSE) +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = ""),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n)) +
    theme_minimal() + 
    theme(legend.position = "bottom"), 
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```
